### 2019-06-28 Memoria/Chapters/Clustering.tex
Correcciones y nuevas secciones

Firstly, it will be necessary to provide an introduction, albeit a brief one, to clustering and its applications, in order to ease the understanding of the following chapters. For this purpose we will follow the study carried out in \cite{Everitt:2009:CA:1538772}.

\section{Reasons for Classifying}

@@

\section{Numerical Methods of Classification}

@@

\subsection{What is a Cluster?} \label{sec:WhatIsCluster}

@@

\section{Applications of Clustering}

>>>>

Firstly, it will be necessary to provide an introduction, albeit a brief one, to clustering and its applications, in order to ease the understanding of the following chapters. For this purpose we will follow the study carried out in \cite{Everitt:2009:CA:1538772}. In Section  \ref{sec:ReasonsClassif} we present the reasons that lead humans to develop automatic classification methods. The numerical formulation for the latter is given in Section \ref{sec:NumMethClassif}. We give an intuitive definition for ``cluster'' in Section \ref{sec:WhatIsCluster}. Lastly a list of clustering application is presented in Section \ref{sec:ClusteringApplications}.

\section{Reasons for Classifying} \label{sec:ReasonsClassif}

@@

\section{Numerical Methods of Classification} \label{sec:NumMethClassif}

@@

\section{What is a Cluster?} \label{sec:WhatIsCluster}

@@

\section{Applications of Clustering} \label{sec:ClusteringApplications}

### 2019-06-28 Memoria/Chapters/ConstrainedClustering.tex
Nuevos capitulos en memoria y correcciones en papers
Correcciones y nuevas secciones

Once the basics concepts about clustering have been introduced, we can focus im defining the concepts related to constrained clustering, as well as to give examples of its application and highlight the benefits and problems presented by its use. To this end we take as our main reference the survey presented in \cite{davidson2007survey}.

\section{Motivation for Constrained Clustering}

@@

\section{Constraints Definition}

@@

\section{Use of Constraints}

@@

Figure \ref{fig:ConstOverDataset} shows a dataset together with its associated constraints. Figure \ref{fig:ClusteringSatAllConst} proposes a possible clustering that satisfies all constraints.

\begin{figure}[bth]
	\myfloatalign
	{\includegraphics[width=.6\linewidth]{gfx/ConstClust/InputInstancesAndConst1}
	\caption[Constraints on a dataset.]{Constraints on a dataset \cite{davidson2007survey}.} \label{fig:ConstOverDataset}
	}
	{\includegraphics[width=.6\linewidth]{gfx/ConstClust/ClusteringSatAll}
	\caption[Clustering satisfying all constraints.]{Clustering satisfying all constraints \cite{davidson2007survey}.} \label{fig:ClusteringSatAllConst}
	}
\end{figure}

@@

Figure \ref{fig:MetricLearned} shows a possible clustering based on a metric learned from the constraints specified in Figure \ref{fig:ConstOverDataset2}. It should be noted that in Figure \ref{fig:MetricLearned} the data space has been compressed on the vertical axis and widened on the horizontal axis to match the learned distance metric.

\begin{figure}[bth]
	\myfloatalign
	{\includegraphics[width=.6\linewidth]{gfx/ConstClust/InputInstancesAndConst2}
	\caption[Constraints on a dataset.]{Constraints on a dataset \cite{davidson2007survey}.} \label{fig:ConstOverDataset2}
	}
	{\includegraphics[width=.6\linewidth]{gfx/ConstClust/MetricaAprendida}
	\caption[Clustering based on a metric learned based on constraints.]{Clustering based on a metric learned based on constraints \cite{davidson2007survey}.} \label{fig:MetricLearned}
	}
\end{figure}

@@

Figure \ref{fig:CMUFacesDatabase} shows a sample from the CMU (Carnegie Mellon University) faces dataset, where the task is to group faces based on different criteria. In this case, the goal is to group the faces according to their orientation.

\clearpage

@@

\section{Benefits of Using Constraints}

@@

\subsection{The Feasibility Problem}

>>>>

Once the basics concepts about clustering have been introduced, we can focus im defining the concepts related to constrained clustering, as well as to give examples of its application and highlight the benefits and problems presented by its use. To this end we take as our main reference the survey presented in \cite{davidson2007survey}. We will start by describing the motivation for constrained clustering in Section \ref{sec:CCMotiv}. We formalize the concept of constraints and discuss their use in Sections \ref{sec:ConstDef} and \ref{sec:ConstUse} respectively. Afterwards a list of constrained clustering application is presented in Section \ref{sec:CCApplications}. Benefits and problems, as well as solutions for these problems, are discussed in Sections \ref{sec:ConstraintsBenefits} and \ref{sec:ConstraintsProblems} respectively.

\section{Motivation for Constrained Clustering} \label{sec:CCMotiv}

@@

\section{Constraints Definition} \label{sec:ConstDef}

@@

\section{Use of Constraints} \label{sec:ConstUse}

@@

Figure \ref{fig:ConstClustOverDataset} shows a dataset together with its associated constraints and proposes a possible clustering that satisfies all constraints.

\begin{figure}[bth]
	\myfloatalign
	\subfloat[Constraints over a dataset.]
	{\includegraphics[width=.45\linewidth]{gfx/ConstClust/InputInstancesAndConst1}}
	\hspace{1cm}
	\subfloat[Clustering satisfying all constraints.]
	{\includegraphics[width=.45\linewidth]{gfx/ConstClust/ClusteringSatAll}}

	\caption[Constraints and clustering over a dataset]{Constraints and clustering over a dataset \cite{davidson2007survey}.} \label{fig:ConstClustOverDataset}
\end{figure}

@@

Figure \ref{fig:ConstrainsAndMetricLearned} shows a possible clustering based on a metric learned from the constraints. It should be noted that in Figure \ref{fig:MetricLearned} the data space has been compressed on the vertical axis and widened on the horizontal axis to match the learned distance metric.

\begin{figure}[bth]
	\myfloatalign
	\subfloat[Constraints over a dataset.]
	{\includegraphics[width=.45\linewidth]{gfx/ConstClust/InputInstancesAndConst2}} 
	\hspace{0.5cm}
	\subfloat[Clustering based on a metric learned from constraints.]
	{\includegraphics[width=.45\linewidth]{gfx/ConstClust/MetricaAprendida}
	\label{fig:MetricLearned}}
	\caption[Clustering based on a metric learned from constraints.]{Clustering based on a metric learned based on constraints \cite{davidson2007survey}.} \label{fig:ConstrainsAndMetricLearned}
\end{figure}

@@

Figure \ref{fig:CMUFacesDatabase} shows a sample from the CMU (Carnegie Mellon University) faces dataset, where the task is to group faces based on different criteria. In this case, the goal is to group faces according to their orientation.

@@

\section{Benefits of Using Constraints} \label{sec:ConstraintsBenefits}

@@

\subsection{The Feasibility Problem} \label{sec:FeasibilityProblem}
